Learning constraints in tabular data

### 2016-05-13 Paper/ECAI/tabular.tex
Cosmetic
Showed bold

\begin{verbatim}
VERY PSEUDOcode:
something recursive that handles vectors/subgroups differently like this?
check(Groups, X, Test):
  if |Groups| == 0:
    forall i in ?: vector elements...
      if not Test(X):
        return []
    return X
  // else
  all = []
  Group = Groups.pop(0)
  if vector(Group):
    forall Vec in Group:
      all += check(Groups, X + Vec, Test)
  else:
    forall Subgroup in Group:
      all += check(Groups, X + Subgroup, Test)
  return all
\end{verbatim}

@@

\caption{Overview of constraint templates implemented in our system, which covers the most popular spreadsheet constraints we encountered. The templates marked with $\dagger$ are aggregate constraint templates, the table shows the version for sum but the implementation also supports max, min, average, product and count. Subgroups in normal font have to be vectors, while subgroups in bold may contain more than one vector.\label{table:constraints}}

>>>>

\begin{verbatim}
VERY PSEUDOcode:
something recursive that handles vectors/
subgroups differently like this?
check(Groups, X, Test):
  if |Groups| == 0:
    forall i in ?: vector elements...
      if not Test(X):
        return []
    return X
  // else
  all = []
  Group = Groups.pop(0)
  if vector(Group):
    forall Vec in Group:
      all += check(Groups, X + Vec, Test)
  else:
    forall Subgroup in Group:
      all += check(Groups, X + Subgroup, Test)
  return all
\end{verbatim}

@@

\caption{Overview of constraint templates implemented in our system, which covers the most popular spreadsheet constraints we encountered. The templates marked with $\dagger$ are aggregate constraint templates, the table shows the version for sum but the implementation also supports max, min, average, product and count. Subgroups in normal font have to be vectors, while subgroups in \textbf{bold} may contain more than one vector.\label{table:constraints}}
